Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-04-01 W13report.tex

In all cases the empirical results are below the predicted results indicating
that the number counts are smaller than the theoretical floor.  This is not entirely unexpected, as each
curve is strongly correlated, being a cumulative distribution, and represents only 9 samplings of the
background random Gaussian field.  We find that we can perform a 1--parameter correction to these curves that
yields both the same slope and zeropoints as the theoretical curves, with the exception of the deconvolution 
visit.  This correction involves scaling {\it down} the variance in the images by 2.5\%, 1.5\% and 1\% for 
v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
in the bottom row of Figure\ref{fig-fp_v_thresh}.  These results suggest our variance estimates 
are too {\it high}, and we are therefore detecting too {\it few} false detections.  This does not agree 
entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, 
which suggest that our variance planes {\it underestimate} the true variance.  However, this makes clear that 
while we are at the level of the theoretical floor in false detection rate, it is imperative to track the 
variance in our data to at the 1\% level or better to optimize both the false detection rate, and the true detection
efficiency. This will be the subject of the Summer 2013 work.

>>>>

In all cases the empirical results are below the predicted results indicating
that the number counts are smaller than the theoretical floor.  This is not entirely unexpected, as each
curve is strongly correlated, being a cumulative distribution, and represents only 9 samplings of the
background random Gaussian field.  We find that we can perform a 1--parameter correction to Equation \ref{eq-theory}
curves that
yields both the same slope and zeropoints as the theoretical curves, with the exception of the deconvolution 
visit.

Specifically, we define:
\begin{equation}
n\prime(>\nu) = n(>k\dot\nu)
\label{correction}
\end{equation}  
For our data we scale {\it down} $\nu$ in the model by $k = 0.975, 0.985 $~and~$ 0.99$ for 
v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
in the bottom row of Figure\ref{fig-fp_v_thresh}.  These results suggest our variance estimates 
are too {\it high}, and we are therefore detecting too {\it few} false detections.  This does not agree 
entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, 
which suggest that our variance planes {\it underestimate} the true variance.  However, this makes clear that 
while we are at the level of the theoretical floor in false detection rate, it is imperative to track the 
variance in our data to at the 1\% level or better to optimize both the false detection rate, and the true detection
efficiency. This will be the subject of the Summer 2013 work.
